$p$-adic precision

### 2014-02-17 padicprec.tex
Work on loc. anal.
Improvement of the loc. anal. part.
Consistent with the latest version of the Main lemma.

Still need work on details like \overline{K} versus K, minoration,
majoration, how to obtain them, and make something pretty...

Let $r \in (0, \delta)$. Let $B^-_E(r) \subset H \subset B_E(r).$ Let us 
show that $f$ maps surjectively $H$ onto $f'(0) (H)$. We first prove 
that $f(H) \subset f'(0) (H)$. Let $x \in H$. By differentiability at 
$0$, $\Vert f(x)-f'(0)(x) \Vert \leq \varepsilon \Vert x \Vert $. 
Therefore, if $y=f(x)-f'(0)(x)$, then $\Vert y \Vert \leq 
\varepsilon r$. By definition of $C$, we have $B_F(\varepsilon r) 
\subset \varepsilon C f'(0) (B_E(r))$. Thus there exists $x_1 \in 
\varepsilon C \cdot B_E(r)$ such that $f'(0) (x_1) =y$. Since 
$\varepsilon C < \rho$, we get $x_1 \in B^-_E(\rho r) \subset H$ and 
then $f(x)= f'(0) (x-x_1) \in f'(0) (H)$.

We shall now prove surjectivity. Let $y \in f'(0) (H)$. Let $x_0 \in H$ 
be such that $y = f'(0) (x_0)$. We define inductively two sequences 
$(x_n)$ and $(z_n)$ as follows:
\begin{itemize}
\item $z_n$ is an element of $E$ satisfying $f'(0)(z_n) = y - 
f(x_n)$ and $\Vert z_n \Vert \leq C \cdot \Vert y - f(x_n) \Vert$ (such 
an element exists by definition of $C$), and
\item $x_{n+1}=x_n+z_n$.
\end{itemize}
For convenience, let us also define $x_{-1} = 0$. We claim that the 
sequences $(x_n)$ and $(z_n)$ are well defined and take their values in 
$H$. To establish this, it is enough to prove that, assuming that 
$x_{n-1}$ and $x_n$ belongs to $H$, so do $z_n$ and $x_{n+1}$. Noticing
that 
\begin{equation}
\label{eq:mainlemma}
y - f(x_n) 
= f(x_{n-1}) + f'(0)(z_{n-1}) - f(x_n)
= f(x_{n-1}) - f(x_n) - f'(0)(x_{n-1} - x_n)
\end{equation}
we deduce using differentiability that
$\Vert y - f(x_n) \Vert \leq \varepsilon \cdot \Vert x_n - x_{n-1}
\Vert$.
Since we are assuming that $x_{n-1}$ and $x_n$ lie in $H \subset
B_E(r)$, we find $\Vert y - f(x_n) \Vert \leq \varepsilon r$. Thus
$\Vert z_n \Vert \leq C \cdot \varepsilon r < \rho r$ and then
$z_n \in H$. From the relation $x_{n+1} = x_n + z_n$, we finally
deduce $x_{n+1} \in H$.

@@

We refer to Schneider \cite{schneider:11a}, \S 6, for a definition of a locally analytic function.

\begin{deftn} \label{deftn :  serie and norm}
Let $f(x)= \sum_{n \geq 0} f_n (x)$ be a serie over $E,$ a complete normed $K$-vector space. We assume that for any $\lambda  \in K,$ $x \in E,$ $n \in \mathbb{N},$ $\vert f_n(\lambda x) \vert = \vert \lambda \vert \vert f_n (x) \vert.$ 
We define $\vert f_n \vert = \sup_{x \in B_E(0,1)} \vert f_n(x) \vert,$ and we assume that all the $\vert f_n \vert $ are finite. We define $R((f_n)_n)$ to be the radius of convergence of the serie.

We also define : \[\Lambda((f_n)_n) (v) = \log \sup_{x \in B(0,e^v)} \vert f(x) \vert.\]
We define  $NP((f_n)_n)$ to be the Newton polygon of $f$, that is to say, the lower convex hull in $\mathbb{R}^2$ of the $(k, - \log \vert f_k \vert ),$ $k\geq 0.$ 
\end{deftn}

@@

\begin{prop} \label{prop : conjugate Newton}
We define $v_\infty \in \mathbb{R} \cup \left\lbrace \infty \right\rbrace$ to be the limit of the slopes of $NP((f_n)_n).$
We denote by $NP((f_n)_n)^*$ the convex conjugate of $NP((f_n)_n).$ $NP((f_n)_n)^*$ is defined over $\left] -\infty,v_{\infty} \right[$ (at least)
\end{prop}

$\Lambda((f_n)_n)$ and $NP((f_n)_n)$ are connected :

\begin{prop} \label{prop : connexion sup Newton}
We have $R((f_n)_n) = e^{v_{\infty}}.$
Moreover, for any $v < \log \left( R((f_n)_n) \right),$ \[ \Lambda ((f_n)_n) (v) = NP((f_n)_n)^*(v).\]
\end{prop}
\begin{proof}
Let $v \in \left] -\infty,v_{\infty} \right[,$ and let us assume that $v$ is not a slope of $NP((f_n)_n).$
Let $u = NP((f_n)_n)^*(v).$ Then the intersection of the line defined by $y=vx-u$ and $NP((f_n)_n)$ is an extreme point of $NP((f_n)_n),$ say $(n, - \log ( \vert f_n \vert ))$ for some $n \geq 0,$ and $u = vn + \log \vert f_n \vert.$

$v$ is not a slope of $NP((f_n)_n)$ and by convexity of $NP((f_n)_n)$, its difference quotients at $n$ are increasing, therefore, there exists some $c>0$ such that for any $m\geq 0,$ $vm-u \leq - \log \vert f_m \vert - c \vert n-m \vert.$ Since $vm-u=vm-vn-log \vert f_n \vert,$ we get $-vn-\log \vert f_n \vert + c \vert n-m \vert  \leq -vm-\log \vert f_m \vert .$

Now, let $x \in  B(0,e^v),$ and $m \geq 0.$ Definition of $\vert f_m$ yields $ \vert f_m (x) \vert \leq \vert f_m \vert e^{vm}.$ Therefore \[\vert f_m (x) \vert \leq e^{-c \vert n-m \vert } \vert f_n \vert  e^{vn}< \vert f_n \vert e^{vn}.\]
Therefore, the serie converges and by ultrametricity $ \vert f(x) \vert \leq \vert f_n \vert e^{vn},$ and $\Lambda ((f_l)_l)(v) \leq \log \left( \vert f_n \vert e^{vn} \right).$ Furthermore,  $R((f_n)_n)  \geq e^v.$

Now, definition of $\vert f_n \vert$  provides $(x_i)_{i\geq 0}$ in $B(0,e^v)$ such that $\lim \vert f_n (x_i)= \vert f_n \vert e^{vn}.$

Since for any $i,$ $\vert f_m (x) \vert \leq e^{-c \vert n-m \vert } \vert f_n \vert  e^{vn},$ then for $i$ large enough, $\vert f_m (x) \vert < \vert f_n (x) \vert $ and $\vert f(x) \vert = \vert f_n (x) \vert.$

As a consequence, $\lim \vert f(x_i) \vert = \vert f_n \vert e^{vn},$ and  $\Lambda ((f_l)_l)(v) = \log ( \vert f_n \vert e^{vn}) = u= NP((f_n)_n)^*(v).$

Therefore, for any $v \in \left] -\infty,v_{\infty} \right[,$ with $v$ not a slope of $NP((f_n)_n),$ we get $\Lambda ((f_l)_l)(v) =NP((f_n)_n)^*(v).$
Since both $\Lambda ((f_l)_l)$ is increasing and $NP((f_n)_n)^*$ is continuous (since it is convex), we deduce that $R((f_n)_n) \geq  e^{v_{\infty}}$ and both functions coincide on $v \in \left] -\infty,v_{\infty} \right[,$

One can show similarily that $R((f_n)_n) \leq  e^{v_{\infty}}.$
\end{proof}

\begin{cor} Let $f(x)= \sum_{n \geq 0} f_n (x)$ and $g(x)= \sum_{n \geq 0} g_n (x)$ be two series as in definition \ref{deftn :  serie and norm}. Let $f(x)g(x)=\sum_{n \geq 0} \mu_n (x) $ and $f \circ g(x)=\sum_{n \geq 0} \tau_n (x) .$ Then :
$\Lambda((f_n+g_n)_n) \leq \max (\Lambda((f_n)_n),\Lambda((g_n)_n))$
$\Lambda((\mu_n)_n) \leq \Lambda((f_n)_n)+\Lambda((g_n)_n)$
$\Lambda((\tau_n)_n) \leq \Lambda((f_n)_n) \circ \Lambda((g_n)_n)$
\end{cor}

@@

\begin{cor} \label{cor : trunc series}
Let $f(x)= \sum_{n \geq 0} f_n (x)$ be a serie as in definition \ref{deftn :  serie and norm}, $n_0 \geq 0$ and $g(x)= \sum_{n \geq n_0} f_n (x).$ Then $\Lambda((g_n)_n) \leq \Lambda((f_n)_n)$ and the slopes of $\Lambda((g_n)_n)$ are bigger than $n_0$. 
As a consequence, a minoration of $\Lambda((g_n)_n)$ can be obtain by extending $\Lambda((f_n)_n)(v)$ with a slope $n_0$ for $v \leq n_0$.
\end{cor}

Now, let $E$ and $F$ be two complete normed $K$-vector spaces, and let $f$ and the $L_k$'s be as in definition \ref{deftn:analyticNP}. We assume $L_1$ is surjective. We define, for any $n \geq 1$, $f_n(x)=L_n(x,\dots,x)$ for any $x \in E.$ 
Let $C$ be given by the Banach-Schauder theorem for $L_1$, $\varepsilon = \frac{1}{C}$. We provide three methods to find a sufficient $r$ for \ref{lem:main}.

For the first one, we assume that we have know a function that majorates $\Lambda((f_n)_{n \geq 1})$.

\begin{prop} \label{prop : maj Lambda} \label{prop:locanalytic}
If $m_1$ is a real convex function above $\Lambda((f_n)_{n \geq 1})$.
We define $m_2$ by extending $m_1$ with slope $2$.
Let $r$ be the abscissa of the intersection of $m_2$ and the line defined by $y=-\log \varepsilon+ x.$ Then $e^r$ is enough for \ref{lem:main}.
\end{prop}
\begin{proof}
$r$ is well-defined thanks to corollary \ref{cor : trunc series}, and $m_2 \geq \Lambda((f_n)_{n \geq 2}).$

One only has to prove that for all $x \in B(0,e^r),$ $\vert \sum_{n\geq 2} f_n(x) \vert \leq \varepsilon \vert x \vert.$

If $x \in B(0,e^r),$ $u = \log \vert x \vert,$ then $\Lambda((f_n)_{n \geq 2})(u) \geq -\log \varepsilon+ u.$
With proposition \ref{prop : connexion sup Newton}, for any $m \geq 2,$ $-\log \vert f_m \vert +m u \geq -\log \varepsilon+ u.$

@@

If we denote by $NP((M_{n+1})_{n \geq 1})$ the lower convex hull of the $(n, -\log M_{n+1})$ for $n \geq 1$, then $r$ such that $-\log \varepsilon=NP((M_n)_{n \geq 2})^*(r)$ is enough.
\end{prop}
\begin{proof}
Same idea as proposition \ref{prop : maj Lambda}. One can define $g_n$ with $g_n (x) =\frac{f_n(x)}{\vert x \vert}$ and $g_n(0)=0$ and work with $\Lambda ((g_n)_n).$
\end{proof}

We finally provide a simple method when working with finite dimension and $p$-adic fields.

\begin{prop} \label{prop : locanalyticfinitedim}
If $f$ is a locally analytic map $K^n \rightarrow K^m$, with $K$ a $p$-adic field, if $C$ and $\varepsilon$ are as above. It is enough to work with the Newton polygon $NP_F$ of $F(t) = \sum_{k\geq 0}^{+\infty} \interleave f^{(k+1)}(0) \interleave  t^k \in \mathbb{R}[[t]]$ : let $r$ be such that $NP_F^* \left( \log_p r - \frac{1}{p-1} \right) \leq \log_p \varepsilon.$ Then $r$ is enough for lemma \ref{lem:main}. 
\end{prop}
\begin{proof}
Same as before, with $L_n=\frac{f^{(n)}(0)}{n!}$ and Legendre formula. The result follows \textit{mutatis mutandis}.
\end{proof}

>>>>

Let $r \in (0, \delta)$. Let $B^-_E(\rho r) \subset H \subset B_E(r).$ Let us 
show that $f$ maps surjectively $H$ onto $f'(0) (H)$. We first prove 
that $f(H) \subset f'(0) (H)$. Let $x \in H$. By differentiability at 
$0$, $\Vert f(x)-f'(0)(x) \Vert \leq \varepsilon \Vert x \Vert $. 
Therefore, if $y=f(x)-f'(0)(x)$, then $\Vert y \Vert \leq 
\varepsilon r$. By definition of $C$, we have $B_F(\varepsilon r) 
\subset \varepsilon C f'(0) (B_E(r))$. Thus there exists $x_1 \in 
\varepsilon C \cdot B_E(r)$ such that $f'(0) (x_1) =y$. Since 
$\varepsilon C < \rho$, we get $x_1 \in B^-_E(\rho r) \subset H$ and 
then $f(x)= f'(0) (x-x_1) \in f'(0) (H)$.

We shall now prove surjectivity. Let $y \in f'(0) (H)$. Let $x_0 \in H$ 
be such that $y = f'(0) (x_0)$. We define inductively two sequences 
$(x_n)$ and $(z_n)$ as follows:
\begin{itemize}
\item $z_n$ is an element of $E$ satisfying $f'(0)(z_n) = y - 
f(x_n)$ and $\Vert z_n \Vert \leq C \cdot \Vert y - f(x_n) \Vert$ (such 
an element exists by definition of $C$), and
\item $x_{n+1}=x_n+z_n$.
\end{itemize}
For convenience, let us also define $x_{-1} = 0$ and $z_{-1}=x_0.$ We claim that the 
sequences $(x_n)$ and $(z_n)$ are well defined and take their values in 
$H$. To establish this, it is enough to prove that, assuming that 
$x_{n-1}$ and $x_n$ belongs to $H$, so do $z_n$ and $x_{n+1}$. Noticing
that 
\begin{equation}
\label{eq:mainlemma}
y - f(x_n) 
= f(x_{n-1}) + f'(0)(z_{n-1}) - f(x_n)
= f(x_{n-1}) - f(x_n) - f'(0)(x_{n-1} - x_n)
\end{equation}
we deduce using differentiability that
$\Vert y - f(x_n) \Vert \leq \varepsilon \cdot \Vert x_n - x_{n-1}
\Vert$.
Since we are assuming that $x_{n-1}$ and $x_n$ lie in $H \subset
B_E(r)$, we find $\Vert y - f(x_n) \Vert \leq \varepsilon r$. Thus
$\Vert z_n \Vert \leq C \cdot \varepsilon r < \rho r$ and then
$z_n \in H$. From the relation $x_{n+1} = x_n + z_n$, we finally
deduce $x_{n+1} \in H$.

@@

We refer to Schneider \cite{schneider:11a}, \S 6, for a definition of a locally analytic function, and we extend it to any complete $K$ vector space :

\begin{deftn} \label{deftn:analyticNP}
Let $E$ and $F$ be two complete ultrametric $K$-Banach spaces. Let $U \subset E$ be an open set.
A function $f \: : \: U \rightarrow F$ is said to be locally analytic if for any $x \in U,$ there exists some open subset $U_x$ of $E$ and some $n$-linear mappings $L_n \: : \: E^n \rightarrow F$ for any $n \geq 1,$ such that : for any $y \in U_x,$ the sum $\sum_{n \geq 1} L_n(y,\dots,y)$ converges in F, and $f(x+y)=f(x)+\sum_{n \geq 1} L_n(y,\dots,y).$
\end{deftn}

We then mostly study such a serie defined at $x$.

\begin{deftn} \label{deftn :  serie and norm}
Let $f(x)= \sum_{n \geq 0} f_n (x)$ be a serie over mappings $E \rightarrow F,$ where $E$ and $F$ are complete normed $\overline{K}$-vector space. We assume that for any $\lambda  \in \overline{K},$ $x \in E,$ $n \in \mathbb{N},$ $\vert f_n(\lambda x) \vert = \vert \lambda \vert \vert f_n (x) \vert.$ 
We define $\vert f_n \vert = \sup_{x \in B_E(0,1)} \vert f_n(x) \vert,$ and we assume that all the $\vert f_n \vert $ are finite. 
We also define, for any $v \in \mathbb{R}$ such that this $\sup$ is finite : \[\Lambda(f) (v) = \log \sup_{x \in B_E(0,e^v)} \vert f(x) \vert,\]
and $\Lambda(f) (v) =+\infty$ otherwise.
We define  $NP(f)$ to be the Newton polygon of $f$, that is to say, the lower convex hull in $\mathbb{R}^2$ of the $(k, - \log \vert f_k \vert ),$ $k\geq 0.$ 
\end{deftn}

@@

\begin{prop} \label{prop : conjugate Newton}
We define $v_\infty \in \mathbb{R} \cup \left\lbrace \infty \right\rbrace$ to be the limit of the slopes of $NP(f).$
We denote by $NP(f)^*$ the convex conjugate of $NP(f).$ $NP(f)^*$ is defined over $\left] -\infty,v_{\infty} \right[$ (at least)
\end{prop}

Then, $\Lambda(f)$ and $NP(f)$ are connected :

\begin{prop} \label{prop : connexion sup Newton}
For any $v \in \left]-\infty, v_\infty \right[,$ \[ \Lambda (f) (v) = NP(f)^*(v).\]
\end{prop}
\begin{proof}
Let $v \in \left] -\infty,v_{\infty} \right[,$ and let us assume that $v$ is not a slope of $NP(f).$
Let $u = NP(f)^*(v).$ Then the intersection of the line defined by $y=vx-u$ and $NP(f)$ is an extreme point of $NP(f),$ say $(n, - \log ( \vert f_n \vert ))$ for some $n \geq 0,$ and $u = vn + \log \vert f_n \vert.$

$v$ is not a slope of $NP(f)$ and by convexity of $NP(f)$, its difference quotients at $n$ are increasing, therefore, there exists some $c>0$ such that for any $m\geq 0,$ $vm-u \leq - \log \vert f_m \vert - c \vert n-m \vert.$ Since $vm-u=vm-vn-log \vert f_n \vert,$ we get $-vn-\log \vert f_n \vert + c \vert n-m \vert  \leq -vm-\log \vert f_m \vert .$

Now, let $x \in  B_E(0,e^v),$ and $m \geq 0.$ Definition of $\vert f_m \vert$ yields $ \vert f_m (x) \vert \leq \vert f_m \vert e^{vm}.$ Therefore \[\vert f_m (x) \vert \leq e^{-c \vert n-m \vert } \vert f_n \vert  e^{vn}< \vert f_n \vert e^{vn}.\]
Thus, the serie converges and by ultrametricity $ \vert f(x) \vert \leq \vert f_n \vert e^{vn},$ and $\Lambda (f)(v) \leq \log \left( \vert f_n \vert e^{vn} \right).$

Now, definition of $\vert f_n \vert$  provides $(x_i)_{i\geq 0}$ in $B_E(0,e^v)$ such that $\lim \vert f_n (x_i) \vert= \vert f_n \vert e^{vn}.$

Since for any $i,$ $\vert f_m (x_i) \vert \leq e^{-c \vert n-m \vert } \vert f_n \vert  e^{vn},$ then for $i$ large enough, $\vert f_m (x_i) \vert < \vert f_n (x_i) \vert $ and $\vert f(x_i) \vert = \vert f_n (x_i) \vert.$

As a consequence, $\lim_i \vert f(x_i) \vert = \vert f_n \vert e^{vn},$ and  $\Lambda (f)(v) = \log ( \vert f_n \vert e^{vn}) = u= NP(f)^*(v).$

Therefore, for any $v \in \left] -\infty,v_{\infty} \right[,$ with $v$ not a slope of $NP(f),$ we get $\Lambda (f)(v) =NP(f)^*(v).$
Since $\Lambda (f)$ is increasing, $NP(f)^*$ is continuous (since it is convex), and $NP(f)$ has only finitely many slopes smaller than $v_\infty-\epsilon$, for any $\epsilon >0$, we deduce that both functions coincide on $v \in \left] -\infty,v_{\infty} \right[,$
\end{proof}

\begin{lem} Let $f(x)= \sum_{n \geq 0} f_n (x)$ and $g(x)= \sum_{n \geq 0} g_n (x)$ be two series as in definition \ref{deftn :  serie and norm}. Then :
\[\Lambda(f+g) \leq \max (\Lambda(f),\Lambda(g))\]
\[\Lambda(f \times g) \leq \Lambda(f)+\Lambda(g)\]
\[\Lambda(f \circ g) \leq \Lambda(f) \circ \Lambda(g)\]
\end{lem}

The following proposition will reveal crucial in order to minorate or majorate $NP(f),$  $NP(f)^*$ or $\Lambda(f),$ and is classical in convex analysis.

@@

\begin{cor} \label{cor : trunc series}
Let $f(x)= \sum_{n \geq 0} f_n (x)$ be a serie as in definition \ref{deftn :  serie and norm}, $n_0 \geq 0$ and $g(x)= \sum_{n \geq n_0} f_n (x).$ Then $\Lambda(g) \leq \Lambda(f)$ and the slopes of $\Lambda(g)$ are bigger than $n_0$. 
As a consequence, a minoration of $\Lambda(g)$ can be obtain by extending $\Lambda(f)(v)$ with a slope $n_0$ for $v \leq n_0$.
\end{cor}

Now, let $E$ and $F$ be two complete normed $K$-vector spaces, and let $f$ and the $L_k$'s be as in definition \ref{deftn:analyticNP}. We assume $L_1$ is surjective. We define, the $\overline{L_k},$ $\overline{E}$ and $\overline{F}$ by extending scalars to $\overline{K}.$ We define for any $n \geq 1$, $f_n(x)=\overline{L_n}(x,\dots,x)$ for any $x \in \overline{E}.$ 
Let $C$ be given by the open mapping theorem for $L_1$, $\rho \in (0, 1]$ and $\varepsilon < \frac{\rho}{C}$. We provide three methods to find a sufficient $\delta$ to define first order lattice as in lemma \ref{lem:main}.

For the first one, we assume that we have know a function that majorates $\Lambda(\sum_{n \geq 1}f_n)$.

\begin{prop} \label{prop : maj Lambda} \label{prop:locanalytic}
If $m_1$ is a real convex function above $\Lambda(\sum_{n \geq 1}f_n)$.
We define $m_2$ by extending $m_1$ with slope $2$.
Let $\delta$ be the abscissa of the intersection of $m_2$ and the line defined by $y=-\log \varepsilon+ x.$ Then $e^\delta$ is enough to define first order lattices as in lemma  \ref{lem:main}.
\end{prop}
\begin{proof}
$\delta$ is well-defined thanks to corollary \ref{cor : trunc series}, and $m_2 \geq \Lambda(\sum_{n \geq 2}f_n).$

It is sufficient to prove that for all $x \in B_{\overline{E}}(0,e^\delta),$ $\vert \sum_{n\geq 2} f_n(x) \vert \leq \varepsilon \vert x \vert.$

If $x \in B_{\overline{E}}(0,e^\delta),$ $u = \log \vert x \vert,$ then $\Lambda( \sum_{n \geq 2}f_n)(u) \geq -\log \varepsilon+ u.$
With proposition \ref{prop : connexion sup Newton}, for any $m \geq 2,$ $-\log \vert f_m \vert +m u \geq -\log \varepsilon+ u.$

@@

If we denote by $NP((M_{n+1})_{n \geq 1})$ the lower convex hull of the $(n, -\log M_{n+1})$ for $n \geq 1$, then $\delta$ such that $-\log \varepsilon=NP((M_n)_{n \geq 2})^*(r)$ is enough to define first order lattices as in lemma  \ref{lem:main}.
\end{prop}
\begin{proof}
Same idea as proposition \ref{prop : maj Lambda}. One can define $g_n$ with $g_n (x) =\frac{f_n(x)}{\vert x \vert}$ and $g_n(0)=0$ and work with $\Lambda ( \sum g_n).$
\end{proof}

We finally provide a simple method when working with finite-dimensional vector spaces over $p$-adic fields.

\begin{prop} \label{prop : locanalyticfinitedim}
If $f$ is a locally analytic map $K^n \rightarrow K^m$, with $K$ a $p$-adic field, if $C,$ $\rho$ and $\varepsilon$ are as above. It is enough to work with the Newton polygon $NP_F$ of $F(t) = \sum_{k\geq 0}^{+\infty} \interleave f^{(k+1)}(0) \interleave  t^k \in \mathbb{R}[[t]]$ : let $r$ be such that $NP_F^* \left( \log_p r - \frac{1}{p-1} \right) \leq \log_p \varepsilon.$ Then $r$ is enough for lemma \ref{lem:main}. 
\end{prop}
\begin{proof}
Same as before, with $L_n=\frac{f^{(n)}(0)}{n!}$ and Legendre formula. The result follows \textit{mutatis mutandis}.
\end{proof}
